%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Work experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------
\vspace{0cm}\begin{cventries}
\cventry
{
\vspace{-0.4cm}
\begin{itemize}
\item Created from scratch and leaded project of Listed Derivatives Clearing UI with back-end layer. Developed logic and presentation for multiple complex flows with high-load data.
\item Managed and educated international team members. Leaded the knolwedge transfer for interns and graduates.
\item Migrated and decomissioned services. Tranfered functionality from Flash, Historic and .NET UIs to common project. 
\item Automated DevOps and testing part of the projects, added CI/CD, fixed penetration testing and OSS vulnarabilities. 
\item Leaded the release process of projects (fully covered > 50 releases), managed the SL3 stream.
\item Created and supported project documentation.
\item Participated in GCP cloud migration process.
\item Added new functionality and fixed bugs in the core platform projects.
\item Contributed to bank-wide design libraries and frameworks.
\end{itemize}
} % Job title
{Deutsche bank / Associate Vice President / Full-stack developer (Java, C\# + TypeScript, React, Redux)/ Remote} % Organization
{} % Location
{June 2019 - Present} % Date(s)	
\noindent	

\vspace{-0.4cm}
\cventry
{
\vspace{-0.4cm}
\begin{itemize}
\item Created from scratch of customized notifications system for bank employees: integrated Slack and Jira.
\item Managed back- and frontend creation streams in a team of 2 people.
\item Automated DevOps and testing part of the projects, added CI/CD. 
\item Created and supported project documentation.
\end{itemize}
} % Job title
{Tinkoff bank / Project manager \& Full-stack developer (Java + TypeScript, Spring Boot, Angular)/ Short-term project} % Organization
{} % Location
{February 2019 - June 2019} % Date(s)	
\noindent	

\vspace{-0.4cm}
\cventry
{
\vspace{-0.4cm}
\begin{itemize}
\item Supported work of IT unit in Spartak stadium (BCC Team).
\item Deployed telecommunication networks in the Grand Kremlin Palace and adjacent territories (BCC Team).
\item Managed radio communication team in Spartak stadium (Spectrum Team).
\end{itemize}
} % Job title
{Confederations Cup - Final Draw of FIFA World Cup - FIFA World Cup / Infrastructure Engineer  - IT Support Leader/ Volunteer} % Organization
{} % Location
{June 2017 - July 2018} % Date(s)	
\noindent	

\vspace{-0.4cm}
\cventry
{
\vspace{-0.4cm}
\begin{itemize}
\item Created from scratch the financial analysis system.
\item Participated in back- and frontend creation in a team of five people.
\item  Managed the SL3 stream.
\end{itemize}
} % Job title
{Sberbank / Full-stack developer (C\#, Asp.NET, JS, HTML)} % Organization
{} % Location
{September 2017 - July 2018} % Date(s)
\noindent	

%\cventry
%{Intern} % Job title
%{EC-leasing} % Organization
%{} % Location
%{February - March 2017} % Date(s)
%{ 
	%\begin{cvitems}
	%	\item {https://github.com/arepina/rtojava}
	%\end{cvitems}
%}

\vspace{-0.4cm}
\cventry
{
\vspace{-0.4cm}
\begin{itemize}
\item Conducted research on the theme <<Building aspect hierarchy based on user reviews about electronic devices>>.
\item Laureate of Student Research Paper Competition held by Higher School of Economics. Nomination <<Best Computer Science research made by undergraduate students>>.
\item Received Presidential and Government awards.
\end{itemize}
} % Job title
{Institute for System Programming RAS / Laboratory assistant (Python)} % Organization
{} % Location
{October 2016 - June 2017} % Date(s)
\noindent	
%------------------------------------------------

%\cventry
%{Trainee analyst } % Job title
%{JSC <<Forecast>>} % Organization
%{} % Location
%{July 2016} % Date(s)
%{ 
	%\begin{cvitems}
%		\item {Business process analysis}
%	\end{cvitems}
%}


\end{cventries}